### 2024-08-13 paper/supplementary.tex
final adjustments to paper before preprint, pending one more change
fixed typo and indent

\noindent\boldblue{\large{Supplementary A: High Variance Results}}
\begin{figure}[H]
    \centering
    \includegraphics[scale =1]{figures/exp1_movement_onset_panel_all_conditions.png}
    \caption*{\boldblue{Supplementary Figure 1: Timing Behaviour.} \boldblue{A)} Average participant movement onset (y-axis) for each experimental condition (x-axis). We found a significant main effect of stimulus movement onset mean (F[1.55,29.48] = 4.36, p = 0.030) and variance (F[1.00,19.00], p = 0.017)) on participant movement onset. There was no significant interaction (F[1.66,31.47], p = 0.565) \boldblue{B)} Corresponding participant movement onset (y-axis) for the three different mean stimulus onsets (x-axis) when collapsed across variance. During the early mean conditions, participants had a high probability of reacting to the stimulus and reaching a target within the time constraint. For the middle mean conditions, participants often waited longer to react and had a later guess than the early mean conditions. Waiting longer to react and/or late guessing led to later movement onset. In the late mean condition, participants waited to react to the stimulus, but ended up guessing a majority of the time (see \boldblue{Supplementary Figure 6}). The combination of waiting for the stimulus and eventually guessing, led to an earlier movement onset compared to the middle mean condition. For both the middle mean and late mean conditions, late guessing often led to indecisions (see \boldblue{Fig. 2}). \boldblue{C)} Participant movement onset standard deviation (y-axis) for each experimental condition (x-axis). We found a significant main effect of mean (F[1.38, 26.28], p = 0.018) and variance (F[1.00,19.00], p < 0.001) on participant movement onset standard deviation There was no significant interaction between stimulus movement onset mean and variance (F[1.98, 37.58], p = 0.097) \boldblue{D)} Corresponding participant movement onset standard deviation (y-axis) for the three different mean onsets (x-axis), when collapsed across variance. In the late mean conditions, waiting to react and then guessing led to a larger movement onset standard deviation compared to the early mean and middle mean conditions. Box and whisker plots display the 25th, 50th, and 75th percentiles. Open circles and connecting lines represent individual data.}
\end{figure}

@@

\newpage
\noindent\boldblue{\large{Supplementary B: Optimal Models}}

We tested three different models to investigate the ability of participants to maximize reward during \boldblue{Experiment 1}: i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (\boldblue{Fig. 2}). Each model represents a different hypothesis on how humans time their decisions, which we address further below. Intuitively, participants should react to the stimulus on trials where it moved earlier in time and guess on trials where it moved later in time. That is, reacting to early stimulus movement onsets ensures they can select the correct target. Likewise, guessing on late stimulus movement onsets affords the participant a 50\% chance of selecting the correct target. However, if participants wait too long to react to a late stimulus movement onset, then they might make too many indecisions and fail to maximize reward.
We modelled the time to switch from reacting to guessing as an optimal transition problem. This differs from past models that have used a similar Bayesian framework, which has beenused to determine reach aim \autocite{trommershauserStatisticalDecisionTheory2003} and reach timing \autocite{hudsonOptimalCompensationTemporal2008}. Here a model represents a decision-maker that selects a transition time, $\tau$. This transition time determines when to stop waiting to react to the stimulus and switch to guessing one of the two targets. The optimal transition time is determined from a decision policy that maximizes reward, given task constraints (i.e. stimulus movement onset distribution and time constraint), and knowledge of sensorimotor delays and uncertainties.

@@

Next we define the mean and standard deviation of the participant movement onset separately for reaction decisions and guess decisions. We begin by defining $S$ as the random variable drawn from the stimulus’s movement onset distribution (\boldblue{Eq. 4}) and $T$ as the random variable drawn from the transition time distribution (\boldblue{Eq. 5}).
% Define random variables S and T
\begin{align}
    S & \sim\mathcal{N}(\mu_{S},\sigma_{S}) \\
    T & \sim\mathcal{N}(\tau,\sigma_{\tau})
\end{align}

>>>>

\noindent\boldblue{\large{Supplementary A: Low and High Variance Results}}
\begin{figure}[H]
    \centering
    \includegraphics[scale =1]{figures/exp1_movement_onset_panel_all_conditions.png}
    \caption*{\boldblue{Supplementary Figure 1: Timing Behaviour.} \boldblue{A)} Average participant movement onset (y-axis) for each experimental condition (x-axis). We found a significant main effect of stimulus movement onset mean (F[1.55,29.48] = 4.36, p = 0.030) and variance (F[1.00,19.00], p = 0.017)) on participant movement onset. There was no significant interaction (F[1.66,31.47], p = 0.565) \boldblue{B)} Corresponding participant movement onset (y-axis) for the three different mean stimulus onsets (x-axis) when collapsed across variance. During the early mean conditions, participants had a high probability of reacting to the stimulus and reaching a target within the time constraint. For the middle mean conditions, participants often waited longer to react and had a later guess than the early mean conditions. Waiting longer to react and/or late guessing led to later movement onset. In the late mean condition, participants waited to react to the stimulus, but ended up guessing a majority of the time (see \boldblue{Supplementary Figure 6}). The combination of waiting for the stimulus and eventually guessing, led to an earlier movement onset compared to the middle mean condition. For both the middle mean and late mean conditions, late guessing often led to indecisions (see \boldblue{Fig. 2}). \boldblue{C)} Participant movement onset standard deviation (y-axis) for each experimental condition (x-axis). We found a significant main effect of mean (F[1.38, 26.28], p = 0.018) and variance (F[1.00,19.00], p < 0.001) on participant movement onset standard deviation There was no significant interaction between stimulus movement onset mean and variance (F[1.98, 37.58], p = 0.097) \boldblue{D)} Corresponding participant movement onset standard deviation (y-axis) for the three different mean onsets (x-axis), when collapsed across variance. In the late mean conditions, waiting to react and then guessing led to a larger movement onset standard deviation compared to the early mean and middle mean conditions. Box and whisker plots display the 25th, 50th, and 75th percentiles. Open circles and connecting lines represent individual data.}
\end{figure}

@@

\newpage
\noindent\boldblue{\large{Supplementary B: Optimal Models}}
\vspace{-1mm}

\noindent We tested three different models to investigate the ability of participants to maximize reward during \boldblue{Experiment 1}: i) No Switch Time Model, ii) Full Switch Time Model and iii) Partial Switch Time Model (\boldblue{Fig. 2}). Each model represents a different hypothesis on how humans time their decisions, which we address further below. Intuitively, participants should react to the stimulus on trials where it moved earlier in time and guess on trials where it moved later in time. That is, reacting to early stimulus movement onsets ensures they can select the correct target. Likewise, guessing on late stimulus movement onsets affords the participant a 50\% chance of selecting the correct target. However, if participants wait too long to react to a late stimulus movement onset, then they might make too many indecisions and fail to maximize reward.
We modelled the time to switch from reacting to guessing as an optimal transition problem. This differs from past models that have used a similar Bayesian framework, which has beenused to determine reach aim \autocite{trommershauserStatisticalDecisionTheory2003} and reach timing \autocite{hudsonOptimalCompensationTemporal2008}. Here a model represents a decision-maker that selects a transition time, $\tau$. This transition time determines when to stop waiting to react to the stimulus and switch to guessing one of the two targets. The optimal transition time is determined from a decision policy that maximizes reward, given task constraints (i.e. stimulus movement onset distribution and time constraint), and knowledge of sensorimotor delays and uncertainties.

@@

Next we define the mean and standard deviation of the participant movement onset separately for reaction decisions and guess decisions. We begin by defining $S$ as the random variable drawn from the stimulus movement onset distribution (\boldblue{Eq. 4}) and $T$ as the random variable drawn from the transition time distribution (\boldblue{Eq. 5}).
% Define random variables S and T
\begin{align}
    S & \sim\mathcal{N}(\mu_{S},\sigma_{S}) \\
    T & \sim\mathcal{N}(\tau,\sigma_{\tau})
\end{align}
